Online {\IterComp}

### 2017-11-17 motivation.tex
minor motivation

    Figure~\ref{fig:motivation_wrong_inputs} highlights what happens when we apply iterative compilation using the wrong set of inputs. We
    selected two distinct subsets of the \textit{KDataSets}~\cite{chen10,chen12a} inputs for the \texttt{tiff2bw} benchmark. Each subset
    has ten inputs. Using iterative compilation we find the best optimization sequence for each subset separately.
    Figure~\ref{fig:motivation_wrong_inputs} shows the speedup over \texttt{-O3} achieved by each sequence when using either of the two
    subsets. Optimization \#1, which was selected using input set \#1, speeds up \texttt{tiff2bw} by 22\% on average when processing set
    \#1, but hurts performance when used with set \#2. Similarly, using optimization \#2 on input set \#1 only improves performance by 5\%,
    much less than what optimization \#1 achieves. In both cases, optimizing the benchmark for the same set it will be evaluated on
    improves performance by 15\% compared to optimizing for some other set. To make iterative compilation profitable, applying it on a
    inputs similar to the ones the application will be used with is absolutely necessary.

    \paragraph{Representative input sets are hard to create.} For developers to create artificial input sets, they first need to know how
    their application is actually being used. This is not always easy or even possible. Then, they need to create data that will trigger a
    similar behavior as when the application is used by users. This needs a deep knowledge of the potential user behavior and
    considerable effort. This will have to be a continuous work in
    progress, to handle changes in the way the application is used.

>>>>

    Figure~\ref{fig:motivation_wrong_inputs} highlights what happens when we apply iterative compilation using the wrong set of inputs. We
    selected two distinct subsets of the \textit{KDataSets}~\cite{chen10,chen12a} inputs for the \texttt{tiff2bw} benchmark. Each subset
    has ten inputs. Using iterative compilation we find the best optimization sequence for each subset separately.
    Figure~\ref{fig:motivation_wrong_inputs} shows the speedup over \texttt{-O3} achieved by each sequence when using either of the two
    subsets. Optimization \#1, which was selected using input set \#1, speeds up \texttt{tiff2bw} by 22\% on average when processing set
    \#1, but hurts performance when used with set \#2. Similarly, using optimization \#2 on input set \#1 only improves performance by 5\%,
    much less than what optimization \#1 achieves. In both cases, optimizing the benchmark for the same set it will be evaluated on
    improves performance by 15\% compared to optimizing for some other set. To make iterative compilation profitable, applying it on
    inputs similar to the ones the application will be used with is absolutely necessary.

    \paragraph{Representative input sets are hard to create.} For developers to create artificial input sets, they first need to know how
    their application is actually being used. This is not always easy or even possible. Then, they need to create data that will trigger a
    similar behavior as when the application is used by users. This needs a deep knowledge of the potential user behavior and
    considerable effort. This will have to be a continuous work in progress, to handle changes in the way the application is used. In some
    areas, such as mobile computing, where developers do not traditionally optimize their applications or provide inputs for performance
    testing, depending on them to provide inputs is a suboptimal choice.
